### 2018-11-27 cv/cv-body.tex
Fix reports

\# Peer-reviewed reports
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. Canadian Science Advisory Secretariat (CSAS)
Research Document. Accepted at regional peer-review meeting October
2018.

@@

>>>>

@@

\hypertarget{peer-reviewed-reports}{%
\section{Peer-reviewed reports}\label{peer-reviewed-reports}}

\begin{description}
\tightlist
\item[2018]
\textbf{Anderson, S.C.}, E.A. Keppel, and A.M. Edwards. A reproducible
data synopsis for over 100 species of British Columbia groundfish.
Canadian Science Advisory Secretariat (CSAS) Research Document. Accepted
at regional peer-review meeting November 2018.
\item[2018]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. Canadian Science Advisory Secretariat (CSAS)
Research Document. Accepted at regional peer-review meeting October
2018.
\end{description}
